Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-25 ms/main.tex
formatting

The frequency of $A$ among parents (i.e. after selection) follows a similar dynamic, but also includes the effect of natural selection, and is therefore
\begin{equation}\label{eq:nextgen_parents}
\begin{aligned}
\bar{w} \tilde{p}' =
& \hat{p}^2 (1+b-c) \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
& \hat{p}(1-\hat{p}) (1-c) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
& (1-\hat{p})\hat{p} (1+b) \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] + \\
& (1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
\end{aligned}
\end{equation}
where fitness values are taken from \autoref{table:prisoner_payoff} and \autoref{table:interactions}, and the population mean fitness is
\begin{equation} \label{eq:mean_fitness}
\bar{w} =  1 + \hat{p}(b-c).
\end{equation}

\autoref{eq:nextgen_parents} can be simplified to
\begin{equation}\label{eq:nextgen_parents_simplified}
\begin{aligned}
\bar{w} \tilde{p}' =
& \hat{p}^2 (1+b-c) \big[1-(1-\hat{p})(1-\alpha)T_B)\big] + \\
& \hat{p}(1-\hat{p}) (1-c) \big[\hat{p}(1-\alpha)T_B+1-T_B \big] + \\
& (1-\hat{p})\hat{p} (1+b) \big[\hat{p}(1-\alpha) + \alpha \big] T_A + \\
& (1-\hat{p})^2 \hat{p} (1-\alpha) T_A \;.
\end{aligned}
\end{equation}
%where $\hat{p}=v\tilde{p}+(1-v)p$.

Finally, we find an equation for the frequency of phenotype $A$ among juveniles in the next generation $\hat{p}'$ as a function of the frequency in the current generation.
Starting from \autoref{eq:horizontal}, we substitute \autoref{eq:nextgen_adults_slimpify} for $p'$ and  \autoref{eq:nextgen_parents_simplified} for $\tilde{p}'$.
We therefore have
\begin{equation} \label{eq:nextgen_juveniles}
\begin{aligned}
\hat{p}' =
& \frac{v}{\bar{w}}\Big[\hat{p}^2(1+b-c)\Big[1-(1-\hat{p})(1-\alpha)T_B)\Big]\Big] + \\
& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1-c)\big( \hat{p}(1-\alpha)T_B + 1 - T_B \big) \Big] + \\
& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1+b)\big(\hat{p}(1-\alpha) + \alpha \big) T_A \Big] + \\
& \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A + \\
& (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B) \;,
\end{aligned}
\end{equation}
where $\bar{w} = 1 + \hat{p}(b-c)$.

\autoref{table:vars_params} summarizes the model variables and parameters.

@@

\begin{figure}[h]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
	~
    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
    ~
    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}

    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries_v_threshold}) are the solid and dashed lines, respectively. 
(\textbf{c})~social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines, respectively.
Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
  	}
    \label{fig:result2}
\end{figure}
%TODO add panel d?

@@

\begin{figure}[h]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
    The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
	In all cases the vertical transmission rate $v$ is on the x-axis.
	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries_v_threshold}) are represented by the solid and dashed lines, respectively. 
    (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively. 
    Horizontal transmission is biased in (\textbf{a,c}) for cooperation, $T_A>T_B$, and in (\textbf{b,d}) for defection, $T_A<T_B$.    
    Here, $T_A = 0.5$, and
    (\textbf{a}) $b=1.2$, , $T_B = 0.4$, $\alpha = 0.4$;
    (\textbf{b}) $b=2$, $T_B = 0.7$, $\alpha = 0.7$;
    (\textbf{c}) $b=1.2$, $T_B = 0.4$, $c=0.5$;
    (\textbf{d}) $b=2$, $T_B = 0.7$, $c=0.5$.
    }
    \label{fig:result3}
\end{figure}

%%% Figure: Spatial model - global selection
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

@@

% Fluctuations in spatial model
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Stable coexistence of both phenotypes in a structured population.}
    The frequency of cooperators (green) and defectors (red) in a structured finite population.
    Both phenotypes start at 50\% frequency.
    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
    }
    \label{fig:spatial_fluctuations}
  \end{figure}

%%% Figure: coexistence map
\begin{figure}[h]
  \centering
    \includegraphics[scale=0.45]{coexistence_without_oblique.pdf}~
    \includegraphics[scale=0.45]{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}
  The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'=\hat{p}$.
  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
  When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.\\
  \textbf{(a)} There is no oblique transmission, $v=1$.
  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries_v_threshold}).
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.\\
  \textbf{(b)} Oblique transmission exists. 
  The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
  }
  \label{fig:coexistence_recursive}
  \end{figure}

%%% Figure: frequency dynamics
\begin{figure}[h]
  \centering
    \includegraphics[scale=0.45]{Time_Figure_Equal_Horizontal.pdf}
    ~\\
    \includegraphics[scale=0.45]{Time_Figure_Only_Vertical_No_Alpha.pdf}
    ~\\
    \includegraphics[scale=0.45]{Time_Figure_No_Vertical.pdf}
  \caption{
  \textbf{Dynamics of the frequency of cooperation.}
  The frequency $\tilde{p}$ of parents with cooperative phenotype $A$ in \textbf{(a-b)} and the frequency $p$ of adults with cooperative phenotype $A$ in \textbf{(c)}.
  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable coexistence of cooperators and defectors (yellow).
  \textbf{(a)} $v=1$, $T_A=T_B=T = 0.2$, $\alpha = 0.5 \neq 0$, $\tilde{p}_0 = 0.5$ and $c=0.1$; \textbf{(b)} $v=1$, $\alpha = 0$, $\tilde{p}^* \approx 0.35$, $T_A = 0.65$, $T_B = 0.1$, $b=1.3$ and $c=0.65$; \textbf{(c)} $v=0$, $\alpha =0.5$, $p_0 = 0.5$, $T_A = 0.5$, $b=1.3$ and $c = 0.5$.
  }
  \label{fig:results}
\end{figure}

>>>>

The frequency of $A$ among parents (i.e. after selection) follows a similar dynamic, but also includes the effect of natural selection, and is therefore
\begin{equation}\label{eq:nextgen_parents}
\begin{aligned}
\bar{w} \tilde{p}' =
& \hat{p}^2 (1+b-c) \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
& \hat{p}(1-\hat{p}) (1-c) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
& (1-\hat{p})\hat{p} (1+b) \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] + \\
& (1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
\end{aligned}
\end{equation}
where fitness values are taken from \autoref{table:prisoner_payoff} and \autoref{table:interactions}, and the population mean fitness is
%\begin{equation} \label{eq:mean_fitness}
$\bar{w} =  1 + \hat{p}(b-c)$.
%\end{equation}
\autoref{eq:nextgen_parents} can be simplified to
\begin{equation}\label{eq:nextgen_parents_simplified}
\begin{aligned}
\bar{w} \tilde{p}' =
& \hat{p}^2 (1+b-c) \big[1-(1-\hat{p})(1-\alpha)T_B)\big] + \\
& \hat{p}(1-\hat{p}) (1-c) \big[\hat{p}(1-\alpha)T_B+1-T_B \big] + \\
& (1-\hat{p})\hat{p} (1+b) \big[\hat{p}(1-\alpha) + \alpha \big] T_A + \\
& (1-\hat{p})^2 \hat{p} (1-\alpha) T_A \;.
\end{aligned}
\end{equation}
%where $\hat{p}=v\tilde{p}+(1-v)p$.
Finally, we find an equation for the frequency of phenotype $A$ among juveniles in the next generation $\hat{p}'$ as a function of the frequency in the current generation.
Starting from \autoref{eq:horizontal}, we substitute \autoref{eq:nextgen_adults_slimpify} for $p'$ and  \autoref{eq:nextgen_parents_simplified} for $\tilde{p}'$.
We therefore have
\begin{equation} \label{eq:nextgen_juveniles}
\begin{aligned}
\hat{p}' =
& \frac{v}{\bar{w}}\Big[\hat{p}^2(1+b-c)\Big[1-(1-\hat{p})(1-\alpha)T_B)\Big]\Big] + \\
& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1-c)\big( \hat{p}(1-\alpha)T_B + 1 - T_B \big) \Big] + \\
& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1+b)\big(\hat{p}(1-\alpha) + \alpha \big) T_A \Big] + \\
& \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A + \\
& (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B) \;.
\end{aligned}
\end{equation}
\autoref{table:vars_params} summarizes the model variables and parameters.

@@

\begin{figure}[p]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
	~
    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
    ~
    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}

    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries_v_threshold}) are the solid and dashed lines, respectively. 
(\textbf{c})~social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
  	}
    \label{fig:result2}
\end{figure}
%TODO add panel d?

@@

\begin{figure}[p]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
    The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
	In all cases the vertical transmission rate $v$ is on the x-axis.
	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries_v_threshold}) are represented by the solid and dashed lines, respectively. 
    (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively. 
    Horizontal transmission is biased in (\textbf{a,c}) for cooperation, $T_A>T_B$, and in (\textbf{b,d}) for defection, $T_A<T_B$.    
    Here, $T_A = 0.5$, and
    (\textbf{a}) $b=1.2$, , $T_B = 0.4$, $\alpha = 0.4$;
    (\textbf{b}) $b=2$, $T_B = 0.7$, $\alpha = 0.7$;
    (\textbf{c}) $b=1.2$, $T_B = 0.4$, $c=0.5$;
    (\textbf{d}) $b=2$, $T_B = 0.7$, $c=0.5$.
    }
    \label{fig:result3}
\end{figure}

%%% Figure: Spatial model - global selection
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

% Fluctuations in spatial model
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Stable coexistence of both phenotypes in a structured population.}
    The frequency of cooperators (green) and defectors (red) in a structured finite population.
    Both phenotypes start at 50\% frequency.
    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
    }
    \label{fig:spatial_fluctuations}
  \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Supplementary Material}
\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/

@@

%%% Figure: coexistence map
\begin{figure}[p]
  \centering
    \includegraphics[scale=0.45]{coexistence_without_oblique.pdf}~
    \includegraphics[scale=0.45]{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}
  The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'=\hat{p}$.
  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
  When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
  \textbf{(a)} There is no oblique transmission, $v=1$.
  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries_v_threshold}).
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
  \textbf{(b)} Oblique transmission exists. 
  The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
  }
  \label{fig:coexistence_recursive}
  \end{figure}

%%% Figure: frequency dynamics
\begin{figure}[p]
  \centering
    \includegraphics[scale=0.45]{Time_Figure_Equal_Horizontal.pdf}
    ~\\
    \includegraphics[scale=0.45]{Time_Figure_Only_Vertical_No_Alpha.pdf}
    ~\\
    \includegraphics[scale=0.45]{Time_Figure_No_Vertical.pdf}
  \caption{
  \textbf{Dynamics of the frequency of cooperation.}
  The frequency $\tilde{p}$ of parents with cooperative phenotype $A$ in \textbf{(a-b)} and the frequency $p$ of adults with cooperative phenotype $A$ in \textbf{(c)}.
  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable coexistence of cooperators and defectors (yellow).
  \textbf{(a)} $v=1$, $T_A=T_B=T = 0.2$, $\alpha = 0.5 \neq 0$, $\tilde{p}_0 = 0.5$ and $c=0.1$; \textbf{(b)} $v=1$, $\alpha = 0$, $\tilde{p}^* \approx 0.35$, $T_A = 0.65$, $T_B = 0.1$, $b=1.3$ and $c=0.65$; \textbf{(c)} $v=0$, $\alpha =0.5$, $p_0 = 0.5$, $T_A = 0.5$, $b=1.3$ and $c = 0.5$.
  }
  \label{fig:results}
\end{figure}
